---
title: "vignette-main"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{vignette-main}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

First we want to load our libraries
```{r setup}
library(plotRs)
library(R.matlab)
```

For our assignment, we want to plot the daily average of 5 chambers for 5 years (2014 to 2018) at our site Turkey Point Deciduous.

Loading the seperate functions from the package
```{r}
#we use two .. to go up a directory then find the folder 
#within windows there is two hidden directories . and .. 
#the . denotes the current directory and .. is used to go up a directory
source("..//R//findAvg.R")
source("../R//readData.R")
```

Now we can use the function we created to read data from a matlab file without referencing the name directly
```{r}
#import data from chamber matlab file
rsIn = readData('..//inst//extdata//chamData.mat')
```

Afterwards, we can find the average of the chambers for 5 years by creating a list that contains the 5 years data points 
```{r}
master = list()
i = 1

while(i<6)
{
  master[[i]] = findAvg(rsIn,i)
  i = i+1
}
```

Now that we have the data, we want to show it in a couple of plots. We start by creating stacked empty data plots.
```{r}
#changing the margins of the data
par(mar = c(1,1,1,1))
par(mfrow=c(5,1))
```

Now we want to run a loop to plot each year within the plots 
```{r}
#number for starting year
year = 2014

#plot the 5 years
for (i in 1:5)
{
  plot(master[[i]], pch = 16, main = year, xlab = "Day of Year", ylab = "Rs (µmol CO2/m2/s)")
  
  #set custom x axis
  axis(1, seq(0,365,25))
  
  #set custom y axis
  axis(2, seq(0,12,2))
  
  year = year+1
}
```
